\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-18 acticle.tex
Add Games Intro

>>>>

\section{Games}
\label{sec:games}
Games can be physical, digital, or even mental. The definition of the word \emph{game} is therefore highly debated, with every book or paper including their own interpretation of what it means for something to be a game. \cite{halfReal} defines a game as a \emph{``rule based formal system''}, a system in which the outcome is not predetermined, stating that there must be interaction with the user in such a way that the user can influence its outcome, causing them to feel emotionally attached to that outcome. \cite{rulesOfPlay} includes nine definitions of the word game, none of which fully agree. The general consensus is that a game involves rules that enforce limitations on the users, it must be goal orientated and involve activities, events, and decision making. The definition given by \cite{artOfGameDesign} provides a nice summary of these definitions: 
\cquote{A Game is a problem-solving activity, approached with a playful
attitude}

This definition appears particularly useful as it is short and to the point, whilst encompassing a number of criteria needed in order for something to be viewed as a game. The use of \textit{problem-solving activity} suggests that there must be some form of challenge within the game, an obstacle for the user to overcome. Games, under this definition, must be interactive, allowing the user to participate and control the flow of play. This means there must be rules governing the bounds of what the user can and cannot do. A \textit{playful attitude} suggests that the user should want to play the game, it should be a fun and interesting experience whilst providing the necessary challenge.

Though the definition provided by \cite{artOfGameDesign} in no way fully expresses what a game is or can be, it appears the most suitable for how the word \emph{game} should be interpreted in the context of this paper, which focusses on digital games. Particular emphasis is placed upon the need for a game to be a playful experience, the user should want to play the game and be fully immersed within its story. Users should not feel like they are being tested or forced to play against their will.
